The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types

### 2023-05-31 final/paper/main.tex
NN NNChain

@@

\section{Main Process}
  The pesudo code of the proposed algorithm to process the dataset is shown below and Fig~\ref{fig:Main_Algo} 
  illurates the process of this algorithm:
  \begin{algorithm}
    \caption{The Main Algorithm}\label{alg:main}
    \begin{algorithmic}[1]
      \Require $\text{Dataset}$
      \State $\text{Data}, \text{Labels} \gets \text{Dataset}$
      \State $\text{Data}' \gets \text{preprocess}(\text{Data})$
      \State $\text{Konwns}, \text{Unkonwns} \gets \text{classify}(\text{Data}')$
      \State $\text{Clusters} \gets \text{clustering}(\text{Unkonwns})$
      \State $\text{Accuracy} \gets \text{calacc}((\text{Konwns}, \text{Clusters}), \text{Labels})$
    \end{algorithmic}
  \end{algorithm}

@@

  On the other hands, neural network classifier has another criterion. First, train a neural network that classify the 
  "konwn" and "unknown". Here "kown" means the types in train data, and "unkown" means the reverse. Then train the other 
  neural network to classify the "konwn" data. The detail is in Algo~\ref{alg:NN}.
  \begin{algorithm}[tb]
    \caption{Neural Network Classification}\label{alg:NN}
    \begin{algorithmic}[1]
      \Require $\text{Train Data, Labels, Test Data}$
      \Assume $\text{Length}(\text{Train Data})=\text{Length}(\text{Labels})=N,\text{Length}(\text{Test Data})=M$
      \State{$\text{Binary NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Mutli-Classification NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Just Knowns, Unkonwns}=\text{Binary NN}.\text{predict}(\text{Test Data})$}
      \State{$\text{Knowns}=\text{Mutli-Classification NN}.\text{predict}(\text{Just Knowns})$}
    \end{algorithmic}
  \end{algorithm}

@@

@@

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: 
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: 
  \item Huang Chia-Yen: Bayes, paper, poster
\end{itemize}

>>>>

\bf{Standardization and Interpolation}: \rm{With} simple interpolation, the dataset size can be easily increased. To ensure that the new produced data would not lower the correctness and precsion of the dataset, standardization to the origin dataset is required.\cite{chen2022doublemix} has used simple interpolation to achieve data augmentation with great outcome. With standardization and interpolation, we earn enough data for the latter machine learning.

@@

\bf{Support Vector Data Description(SVDD)}:  \rm{SVDD} is an unsupervised learning algorithm used for one-class classification or outlier detection. It defines a hypersphere in the feature space to include some specific data to classify one class from other classes. With Deep SVDD, which is the variant of the SVDD which utilize the deep learning, more precise classification can be achieved providing only one class data.\cite{perera2021oneclass} give us the precise explanation how to train a model to classify data with only one class.

\bf{Nearest neighbor chain(NN-Chain)}: \rm{NN-Chain} is data clustering algorithm developed by Jean-Paul Benzécri and J. Juan\cite{Benzécri1982}. This method cluster the data by merge mutual nearest neighbors nodes to one node, and repeat the same action until the goal clustering number is achieved. While the distance can be earned by the normal Euclidean distance, some distance approach is used in the algorithm as well to suit some specific data.\cite{10.1093/comjnl/26.4.354}\cite{müllner2011modern}. NN-Chain is one of the hierarchical clustering algorithm which is likely to be presented in tree-like data structure.
\section{Main Process}
  The pesudo code of the proposed algorithm to process the dataset is shown below and Fig~\ref{fig:Main_Algo} 
  illurates the process of this algorithm:
  \begin{algorithm}
    \caption{The Main Algorithm}\label{alg:main}
    \begin{algorithmic}[1]
      \Require $\text{Dataset}$
      \State $\text{Data}, \text{Labels} \gets \text{Dataset}$
      \State $\text{Data}' \gets \text{preprocess}(\text{Data})$
      \State $\text{Konwns}, \text{Unkonwns} \gets \text{classify}(\text{Data}')$
      \State $\text{Clusters} \gets \text{clustering}(\text{Unkonwns})$
      \State $\text{Accuracy} \gets \text{calacc}((\text{Konwns}, \text{Clusters}), \text{Labels})$
    \end{algorithmic}
  \end{algorithm}

@@

  On the other hands, neural network classifier has another criterion. First, train a neural network that classify the 
  "konwn" and "unknown". Here "kown" means the types in train data, and "unkown" means the reverse. Then train the other 
  neural network to classify the "konwn" data. The detail is in Algo~\ref{alg:NN}.
  \begin{algorithm}[tb]
    \caption{Neural Network Classification}\label{alg:NN}
    \begin{algorithmic}[1]
      \Require $\text{Train Data, Labels, Test Data}$
      \Assume $\text{Length}(\text{Train Data})=\text{Length}(\text{Labels})=N,\text{Length}(\text{Test Data})=M$
      \State{$\text{Binary NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Mutli-Classification NN}.\text{train(Train Data, Labels)}$}
      \State{$\text{Just Knowns, Unkonwns}=\text{Binary NN}.\text{predict}(\text{Test Data})$}
      \State{$\text{Knowns}=\text{Mutli-Classification NN}.\text{predict}(\text{Just Knowns})$}
    \end{algorithmic}
  \end{algorithm}
  During the known-unknown classification, the SVDD is used. First define a model , input every data into it to get the outcome, then use the mean of the outcome as the center of the hypersphere. Then, train the model to make every data in the dataset approach to the center of the hypersphere as close as possible. After training, we can get the radius of the hypersphere, which can be define according to the outcome of the model. Using the radius, we can classify the data to "known", if the distance between the center and the data is less than or equal to the radius, or to "unknown" otherwise.

@@

  For the NN part, SVDD cannot be trained with data only processed interpolation. The hypersphere that the SVDD defines will include all the data in the test dataset, which make the clustering impossible. On the other hand, NN classifying can achieve accuracy 100 percent correctness, so the accuracy of Interpolation~NN with gene expression cancer RNA-Seq dataset will be 64.45 percent, in which only known class is predicted correctly.

  On the other hand,SVDD can be trained with PCA-100-dimension data with accuracy up to 98 percent. With the NN with 100 percent accuracy and clustering algorithm NN-chain processing gene expression cancer RNA-Seq dataset,the accuray can achieve 75 percent correctness.

@@

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: NN, SVDD, NN-Chain, paper, ppt
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: 
  \item Huang Chia-Yen: Bayes, paper, poster
\end{itemize}
